---
title: "Packages, tools and paradigms"
author: "Rudy Pastel"
date: "`r format(Sys.time(), '%A %d %B %Y')`"
output: 
  rmarkdown::html_vignette:
  html_document:
    fig_caption: false
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
vignette: >
  %\VignetteIndexEntry{Packages, tools and paradigms}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(landlord)
```

`landlord` helps me hone my craft by providing an opportunity to learn and 
hopefully master packages, tools and paradigms. Typically, inspiration
is taken from these references manuals.

* [Manuals on CRAN](https://cran.r-project.org/manuals.html)
* [R Packages](https://r-pkgs.org/)
* [Advanced R](https://adv-r.hadley.nz/)
* [R for data science](https://r4ds.had.co.nz/)
* [Extending R](https://www.routledge.com/Extend-ing-R/Chambers/p/book/9781498775717)
* [Mastering Shiny](https://mastering-shiny.org/)
* [Engineering with Shiny](https://engineering-shiny.org/)

This is furthermore a way to demonstrate competence to potential customers.

## Object Oriented Programming (OOP)

As I bring R code to production, a basic understanding of OOP can support more 
effective communication with software engineers and richer software design.
In [Advanced R](https://adv-r.hadley.nz/index.html), [Hadley Wickham](https://hadley.nz/)
presents various ways to do [OOP in R](https://adv-r.hadley.nz/oo.html#oop-in-r).
I chose to focus on R6 in this project because

1. R6 benefits from a full fledged [documentation](https://r6.r-lib.org/)
1. R6 resembles OOP in Python which fellows data scientist often use
1. S4 seems too strict a start point for such a simple project
1. S3 seems so simple as to be tested in client project

In practice, investors, properties and objects are implemented as R6 classes and
combined into a the investment R6 class.

## REST API

