---
title: "Design"
author: "Rudy Pastel"
date: "`r format(Sys.time(), '%A %d %B %Y')`"
output: 
  rmarkdown::html_vignette:
  html_document:
    fig_caption: false
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
vignette: >
  %\VignetteIndexEntry{design}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(landlord)
```

Planning ahead improves software engineering by informing thought through design
choices. This vignette documents these choices and there rationales.


## Users, UX and deployment

[Engineering with Shiny](https://engineering-shiny.org/) suggests to think ahead
users, UX and deployment.

### Personnas

Rudy, Ralph and Jeremy are three cousins interested in real estate investments.
They want to identify worthwhile opportunities by evaluating simple indicators.


* Jeremy has real estate investment experience: he can name indicators of interest
to evaluate investments. He is a fitness coach and has no technical knowledge.
* Ralph is new to real estate investment and wants very safe investments.
Ralph is a product manager and will have suggestions about UX. He can however
not program.
* Rudy is new to real estate investment and is willing to loose some money to learn.
Rudy studied mathematics, is tech literate and actually programs `landlord`.

### Device used to browse the app


For three users, developing for multiple devices would be excessive. The app
will be made for desktop use. Other devices may be considered later for practice
sake.


### Deployment

The app will be publicly accessible on [www.shinyapps.io](https://www.shinyapps.io/)
in the free tier. The code will be public available on 
[Github](https://github.com/RudyPastel/landlord).


## Object Oriented Programming (OOP)

As I bring R code to production, a basic understanding of OOP can support more 
effective communication with software engineers and richer software design.
In [Advanced R](https://adv-r.hadley.nz/index.html), [Hadley Wickham](https://hadley.nz/)
presents various ways to do [OOP in R](https://adv-r.hadley.nz/oo.html#oop-in-r).
I chose to focus on R6 in this project because

1. R6 benefits from a full fledged [documentation](https://r6.r-lib.org/)
1. R6 resembles OOP in Python which fellows data scientist often use
1. S4 seems too strict a start point for such a simple project
1. S3 seems so simple as to be tested in client project

In practice, investors, properties and objects are implemented as R6 classes and
combined into a the investment R6 class.

## REST API

## References

* [Manuals on CRAN](https://cran.r-project.org/manuals.html)
* [R Packages](https://r-pkgs.org/)
* [Advanced R](https://adv-r.hadley.nz/)
* [R for data science](https://r4ds.had.co.nz/)
* [Extending R](https://www.routledge.com/Extend-ing-R/Chambers/p/book/9781498775717)
* [Mastering Shiny](https://mastering-shiny.org/)
* [Engineering with Shiny](https://engineering-shiny.org/)
