---
title: "The landlord package: decide whether a rental property investment is profitable"
author: "Rudy Pastel"
date: "`r format(Sys.time(), '%A %d %B %Y')`"
output: 
  rmarkdown::html_vignette:
  html_document:
    fig_caption: false
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
vignette: >
  %\VignetteIndexEntry{intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(landlord)
```


`landlord` helps budding investor in their first steps. For an investor, 
a property and a loan, it calculates future cash flows and profitability. 
For convenience sake, this can be done via a Shiny dashboard too. 


## Investor

The investor is currently modeled by the maximal down payment he is willing to invest
and how much monthly pay he is will to commit to the bank.
Future investor features may be his age, profession and free cash flow.

## Property

The property is currently modeled only in terms of money

*   Purchase price
*   Renovation costs
*   Legal fees
*   Realtor fees
*   Potential rental income

Future property features may be its age, location and attractiveness.


## Loan

The loan is a [fixed-rate mortgage (FRM)]{https://en.wikipedia.org/wiki/Fixed-rate_mortgage}.
Either the monthly payment is set or the loan term i.e. its duration is fixed.
